---
title: "Affinity propagation clustering analysis"
output: html_document
---

APClustering fig
==============================

Panels for cluster statistics and hierarchical clustering of exemplars, focusing on central brain and some other examples.

```{r startup, echo=FALSE,message=FALSE, warning=FALSE}
source("../../R/StartUp.R")
source("../../R/DivideVPNsCentralBrain.R")
opts_chunk$set(message=FALSE, fig.height=21.8/25.4, fig.width=36.334/25.4, dpi=300, dev='png', fig.path="figure/")
knit_hooks$set(custom.plot = hook_rgl) #Needed to embed plots
par3dmini=c("FOV", "userMatrix", "scale", "zoom")
nopen3d()
```

```{r remote-score-matrix}
# This score matrix is loaded in DivideVPNsCentralBrain.R
options(flycircuit.scoremat=AP_score_mat)
```

Use affinity propagaton to cluster the Flycircuit neurons.

Plot mean cluster score vs cluster size.
```{r ClusterSizeVsScore, fig.width=78.151/25.4*4, fig.height=46.363/25.4*4, cache=TRUE}
csize=table(as.integer(clusterp0$exemplar))

clustersim<-function(gns,summaryfun=mean){
     if(length(gns)==1) return(NA)
      summaryfun=match.fun(summaryfun)
      dmat=fc_nblast(gns,gns,normalisation="mean")
      dmat[upper.tri(dmat)]
      summaryfun(dmat)
   }
mcsim=by(clusterp0$item,clusterp0$exemplar,clustersim)
summary(mcsim)
clstats=qplot(as.vector(mcsim),as.vector(csize), size=I(8), alpha=I(0.3), xlab="Mean cluster score", ylab="Cluster size  (log)")+scale_y_sqrt()+ theme(axis.text.x=element_text(size=22), axis.text.y=element_text(size=22), axis.title.x=element_text(size=26), axis.title.y=element_text(size=26))
par(mar=c(0,2,0,0))
plot(clstats)
```

The 5 clusters (exemplars) with the lower mean similarity are:
```{r low_sim_clusters}
mcsim[names(which(mcsim<0.25))]
```

Plot all exemplars.
```{r AllExemplars, custom.plot=TRUE, fig.width=16.923/25.4, fig.height=10.231/25.4, cache=TRUE}
ex=names(apres16k.p0@exemplars)
plot3d(FCWB)
op=structure(list(FOV = 0, userMatrix = structure(c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0, -1, 0, 0, 0, 0, 1), .Dim = c(4L, 4L)), scale = c(1, 1, 1), zoom = 0.52093118429184), .Names = c("FOV", "userMatrix", "scale", "zoom"))
par3d(op)
plot3d(ex)
```

To improve distinction of major neuronal subtypes obtained in the dendrogram groups, we'll do the hierarchical clustering in only the central brain neurons, removing all optic lobe ones.

Dividing between central brain neurons (cb neurons) and optic lobe ones, k=3: 
```{r HC_of_exemplars_3groups, fig.width=140.033/25.4*1.5, fig.height=36.783/25.4*1.5, cache=TRUE}
par(mar=c(0,2,0,0))
plot(exemhcd)
abline(h=height_for_ngroups(exemhc, k=3), lty='dashed')
```

Plot group 1.
```{r cb_exgroups1, custom.plot=TRUE, fig.width=16.923/25.4, fig.height=10.231/25.4, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3d(subset(exemhc, k=3, groups=1), soma=T, col="red")
```

Plot group 2.
```{r cb_exgroups2, custom.plot=TRUE, fig.width=16.923/25.4, fig.height=10.231/25.4, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3d(subset(exemhc, k=3, groups=2), soma=T, col="green")
```

Plot group 3.
```{r cb_exgroups3, custom.plot=TRUE, fig.width=16.923/25.4, fig.height=10.231/25.4, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3d(subset(exemhc, k=3, groups=3), soma=T, col="blue")
```

Central brain neurons are in groups 2 and 3.

From central brain group, there only a few exemplars in OL that still need to be removed.
```{r removing_central_brain_strays, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3d(olextra, soma=T)
```

The central brain exemplars that will be used from here on. 

There are `r length(excb)` exemplars corresponding to `r length(subset(clusterp0, exemplar%in%excb)$item)` neurons.
```{r final_cb_ex, custom.plot=TRUE, fig.width=30.6144/25.4, fig.height=18.344/25.4, cache=TRUE}
cbg2=setdiff(subset(exemhc, k=3, groups=2), olextra)
cbg3=setdiff(subset(exemhc, k=3, groups=3), olextra)
clear3d()
plot3d(FCWB)
par3d(op)
plot3d(cbg2, soma=T, col='green')
plot3d(cbg3, soma=T, col='blue')
```

Organise these central brain exemplars by hierarchical clustering.

Looking at dendrogram, divided it at h=3. This resulted in similar groups to using all neurons and cutting at h=3 (24 groups). Also tried cutting further, at h=2.5 (19 groups).

But changed cutting level to get large superclasses, using k=14.
```{r HC_cbex, fig.width=181.681/25.4*1.5, fig.height=47.839/25.4*1.5, cache=TRUE}
excbhc=hclustfc(excb)
excbhc$height=sqrt(excbhc$height)
excbhch=colour_clusters(excbhc, k=14, groupLabels=as.roman)
labels(excbhch)=NULL
par(mar=c(0,2,0,0))
plot(excbhch)
abline(h=height_for_ngroups(excbhc, k=14), lty='dashed')
```

Group 1: Central complex group.
```{r cbex_group1, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=1), col=rainbow(14)[1], soma=T)
```

Group 2: P1 neurons.
```{r cbex_group2, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=2), col=rainbow(14)[2], soma=T)
```

Group 3: SMP, SIP.
```{r cbex_group3, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=3), col=rainbow(14)[3], soma=T)
```

Group 4: Mushroom body (gamma, alpha'/beta').
```{r cbex_group4, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=4), col=rainbow(14)[4], soma=T)
```

Group 5: Mushroom body (alpha/beta).
```{r cbex_group5, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=5), col=rainbow(14)[5], soma=T)
```

Group 6: Ventral protocerebrum and SEZ.
```{r cbex_group6, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=6), col=rainbow(14)[6], soma=T)
```

Group 7: Ventral protocerebrum.
```{r cbex_group7, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=7), col=rainbow(14)[7], soma=T)
```

Group 8: Saddle and wedge.
```{r cbex_group8, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=8), col=rainbow(14)[8], soma=T)
```

Group 9: Mix of neurons, octopaminergic neuron.
```{r cbex_group9, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=9), col=rainbow(14)[9], soma=T)
```

Group 10: Midline bilateral and SEZ.
```{r cbex_group10, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=10), col=rainbow(14)[10], soma=T)
```

Group 11: uPNs.
```{r cbex_group11, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=11), col=rainbow(14)[11], soma=T)
```

Group 12: local PN's, 1 uPN, LAL neurons.
```{r cbex_group12, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=12), col=rainbow(14)[12], soma=T)
```

Group 13: SLP and LH.
```{r cbex_group13, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=13), col=rainbow(14)[13], soma=T)
```

Group 14: VLP neurons.
```{r cbex_group14, custom.plot=TRUE, cache=TRUE}
clear3d()
plot3d(FCWB)
par3d(op)
plot3dfc(subset(excbhc, k=14, group=14), col=rainbow(14)[14], soma=T)
```

Add example panels for VPNs
---------------

Adding a couple of panels in supercluster fig to show separation of VPNs. 

Using hierarchical clustering from unilateral VPN clusters: LC10B neurons, and LC4.


### First panel:group 3, representing LC10B

Collect neurons from groups 3 and 4 in VPNs (LC10B, figure 5B). 
```{r vpns_LC10B}
# dput(subset(hc2,k=7,groups=3:4))
g3_4aotu=c("GadMARCM-F000369_seg001", "ChaMARCM-F000333_seg001", "FruMARCM-M002517_seg001", 
"ChaMARCM-F000887_seg002", "ChaMARCM-F001451_seg002", "ChaMARCM-F000700_seg003", 
"FruMARCM-M002548_seg001", "FruMARCM-F000718_seg001", "FruMARCM-M000040_seg001", 
"ChaMARCM-F001149_seg001", "ChaMARCM-F000668_seg002", "FruMARCM-M001848_seg001", 
"FruMARCM-F000366_seg001", "ChaMARCM-F000340_seg001", "FruMARCM-F000577_seg002", 
"FruMARCM-M001983_seg001", "ChaMARCM-F001206_seg001", "ChaMARCM-F000314_seg001", 
"ChaMARCM-F000892_seg001", "FruMARCM-M001516_seg001", "ChaMARCM-F001367_seg001", 
"FruMARCM-M000861_seg001", "FruMARCM-F000688_seg002", "GadMARCM-F000310_seg002", 
"ChaMARCM-F000204_seg002", "ChaMARCM-F001531_seg001", "FruMARCM-M001360_seg001", 
"FruMARCM-M000635_seg001", "ChaMARCM-F000686_seg002", "FruMARCM-M002573_seg003", 
"ChaMARCM-F000272_seg001", "ChaMARCM-F000367_seg001", "ChaMARCM-F000329_seg001", 
"FruMARCM-F001272_seg001", "FruMARCM-F000555_seg002", "FruMARCM-F000569_seg001", 
"FruMARCM-F000560_seg001", "FruMARCM-M000114_seg001", "ChaMARCM-F000018_seg001", 
"ChaMARCM-F000450_seg002", "ChaMARCM-F000960_seg001", "FruMARCM-F001140_seg001", 
"FruMARCM-F001607_seg001", "ChaMARCM-F001136_seg001", "GadMARCM-F000673_seg002", 
"ChaMARCM-F001189_seg001", "FruMARCM-F002104_seg001", "FruMARCM-F001510_seg001", 
"ChaMARCM-F000449_seg003", "ChaMARCM-F001214_seg001", "FruMARCM-F002341_seg001", 
"FruMARCM-M002031_seg001", "FruMARCM-F001534_seg001", "FruMARCM-F000078_seg001", 
"FruMARCM-F000717_seg001", "FruMARCM-F002190_seg001", "ChaMARCM-F000410_seg001", 
"FruMARCM-F002355_seg001", "FruMARCM-F000489_seg001", "FruMARCM-M001553_seg002", 
"FruMARCM-M002520_seg001", "FruMARCM-M002019_seg001", "FruMARCM-M002411_seg001", 
"FruMARCM-F002070_seg001", "ChaMARCM-F000334_seg001", "ChaMARCM-F000559_seg001", 
"FruMARCM-F002149_seg002", "FruMARCM-F001643_seg001", "FruMARCM-F002340_seg001", 
"FruMARCM-F001622_seg001", "FruMARCM-M001691_seg002", "FruMARCM-F000751_seg001", 
"FruMARCM-F001645_seg002", "FruMARCM-M002508_seg002", "FruMARCM-M001438_seg002", 
"FruMARCM-F000511_seg001", "FruMARCM-F000791_seg001", "FruMARCM-M000349_seg004", 
"FruMARCM-M000534_seg001", "FruMARCM-M000871_seg001", "FruMARCM-M000885_seg001", 
"FruMARCM-M002053_seg001", "FruMARCM-M000643_seg002", "npfMARCM-F000007_seg001", 
"ChaMARCM-F000561_seg002", "FruMARCM-F002050_seg001")
```

Find the corresponding clusters and plot the exemplars.
```{r vpns_LC10B-clexonly, custom.plot=TRUE, cache=TRUE}
g3_4aotucl=subset(clusterp0, item%in%g3_4aotu)$cluster
clear3d()
op=structure(list(FOV = 0, userMatrix = structure(c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0, -1, 0, 0, 0, 0, 1), .Dim = c(4L, 4L)), scale = c(1, 1, 1), zoom = 0.816845893859863), .Names = c("FOV", "userMatrix", "scale", "zoom"))
par3d(op)
plot3d(apres16k.p0, plot="ex", clusters=g3_4aotucl, soma=T)
drawRegionSurf("AOTU_L", FCWBNP.surf, alpha=0.3)
```

It corresponds to `r length(unique(g3_4aotucl))` different clusters, and `r length(subset(clusterp0, cluster%in%unique(g3_4aotucl))$item)`, neurons. 

Plot all neurons. There are differences in AOTU and lobula lamination.

```{r vpns_LC10B-clall, custom.plot=TRUE, cache=TRUE}
clear3d()
par3d(op)
plot3d(apres16k.p0, plot="all", clusters=unique(g3_4aotucl), soma=T)
```

### Second panel: group C, representing LC4. 

Collect neurons from group C in VPNs (LC4, figure S4B). 
```{r vpns_LC4}
# dput(subset(hc,k=7,groups=3))
gcpvlp=c("DvGlutMARCM-F004472_seg001", "DvGlutMARCM-F003871_seg001", 
"DvGlutMARCM-F003801_seg001", "ChaMARCM-F001546_seg001", "ChaMARCM-F000737_seg001", 
"DvGlutMARCM-F1355_seg1", "DvGlutMARCM-F1293_seg1", "DvGlutMARCM-F002969_seg001", 
"DvGlutMARCM-F003234_seg001", "DvGlutMARCM-F002799_seg001", "DvGlutMARCM-F1528_seg1", 
"DvGlutMARCM-F1336_seg1", "DvGlutMARCM-F559-X3_seg2", "DvGlutMARCM-F003874_seg001", 
"DvGlutMARCM-F004340_seg001", "DvGlutMARCM-F003147_seg001", "DvGlutMARCM-F1269_seg1", 
"DvGlutMARCM-F004446_seg001", "DvGlutMARCM-F004061_seg001", "DvGlutMARCM-F002401_seg002", 
"DvGlutMARCM-F004570_seg001", "DvGlutMARCM-F003718_seg001", "DvGlutMARCM-F003772_seg001", 
"DvGlutMARCM-F050_seg1", "DvGlutMARCM-F2197_seg1", "ChaMARCM-F000394_seg001", 
"ChaMARCM-F001502_seg002", "GadMARCM-F000401_seg003", "DvGlutMARCM-F756_seg1", 
"ChaMARCM-F000586_seg001", "DvGlutMARCM-F004592_seg002", "DvGlutMARCM-F002754_seg001", 
"DvGlutMARCM-F003885_seg001", "ChaMARCM-F001399_seg001", "DvGlutMARCM-F1254_seg1", 
"GadMARCM-F000524_seg001", "DvGlutMARCM-F003628_seg001", "DvGlutMARCM-F2088_seg1", 
"ChaMARCM-F001108_seg001", "DvGlutMARCM-F003021_seg002", "GadMARCM-F000649_seg001", 
"DvGlutMARCM-F1949_seg1", "DvGlutMARCM-F1038_seg1", "DvGlutMARCM-F454_seg1", 
"DvGlutMARCM-F002872_seg001", "ChaMARCM-F000721_seg001", "ChaMARCM-F001212_seg001", 
"DvGlutMARCM-F003104_seg001", "ChaMARCM-F001457_seg001", "DvGlutMARCM-F002625_seg001", 
"ChaMARCM-F000417_seg001", "DvGlutMARCM-F1116_seg1", "DvGlutMARCM-F003304_seg002", 
"DvGlutMARCM-F1333_seg1")
```

Find the corresponding clusters and plot the exemplars.
```{r vpns_LC4-clexonly, custom.plot=TRUE, cache=TRUE}
gcpvlpcl=subset(clusterp0, item%in%gcpvlp)$cluster
clear3d()
op2=structure(list(FOV = 0, userMatrix = structure(c(1, 0, 0, 0, 
0, -1, 0, 0, 0, 0, -1, 0, -11.4635500555421, -0.745612625663597, 
0, 1), .Dim = c(4L, 4L)), scale = c(1, 1, 1), zoom = 0.777948498725891), .Names = c("FOV", 
"userMatrix", "scale", "zoom"))
par3d(op2)
plot3d(apres16k.p0, plot="ex", clusters=unique(gcpvlpcl), soma=T)
drawRegionSurf("PVLP_L", FCWBNP.surf, alpha=0.3)
drawRegionSurf("PLP_L", FCWBNP.surf, alpha=0.3)
```

It corresponds to `r length(unique(gcpvlpcl))` different clusters, `r length(subset(clusterp0, cluster%in%unique(gcpvlpcl))$item)` neurons. Plot all neurons.
```{r vpns_LC4-clexall, custom.plot=TRUE, cache=TRUE}
clear3d()
op3=structure(list(FOV = 0, userMatrix = structure(c(0.999868869781494, 
0.00186994869727641, -0.016085110604763, 0, 0.00180982786696404, 
-0.999991297721863, -0.00375140830874443, 0, -0.016091987490654, 
0.0037218052893877, -0.999863564968109, 0, -15.4872700977799, 
-0.625269142305341, 0.245943263173103, 1), .Dim = c(4L, 4L)), 
    scale = c(1, 1, 1), zoom = 0.526546359062195), .Names = c("FOV", 
"userMatrix", "scale", "zoom"))
par3d(op3)
plot3d(apres16k.p0, plot="all", clusters=unique(gcpvlpcl), soma=T)
```

Add panels of auditory neurons AMMC-IVLP PN1
---------------------------------------------
From the matching to Lai et al. (2012) in the figure on Auditory Neuron types, find which clusters correspond to AMMC-IVLP PN1.

```{r collect_AMMCIVLPPN1_neurons, cache=TRUE}
ammcivlppn1=
 c("FruMARCM-M001361_seg001", "TPHMARCM-1012M_seg1", "TPHMARCM-M001551_seg003", 
 "TPHMARCM-863M_seg1", "TPHMARCM-102M_seg1", "TPHMARCM-183M_seg1", 
 "TPHMARCM-191M_seg1", "TPHMARCM-456M_seg1", "TPHMARCM-660M_seg2", 
 "TPHMARCM-773M_seg1", "FruMARCM-F001027_seg002", "DvGlutMARCM-F003336_seg001", 
 "DvGlutMARCM-F003157_seg001", "FruMARCM-F000272_seg001", "TPHMARCM-1178F_seg1", 
 "TPHMARCM-1195F_seg1", "TPHMARCM-1213F_seg1", "TPHMARCM-1271F_seg1", 
 "TPHMARCM-1274F_seg1", "TPHMARCM-1283F_seg1", "TPHMARCM-722F_seg1", 
 "TPHMARCM-783F_seg1", "TPHMARCM-800F_seg1", "TPHMARCM-440F_seg1", 
 "TPHMARCM-579F_seg1", "TPHMARCM-691F_seg1", "TPHMARCM-M001633_seg002", 
 "TPHMARCM-1316M_seg1", "TPHMARCM-M001357_seg001", "TPHMARCM-M001364_seg001", 
 "TPHMARCM-M001521_seg001", "TPHMARCM-533M_seg1", "TPHMARCM-560M_seg1", 
 "TPHMARCM-804M_seg1", "TPHMARCM-1197F_seg1", "TPHMARCM-1206F_seg1", 
 "TPHMARCM-1229F_seg1", "TPHMARCM-1234F_seg1", "TPHMARCM-1239F_seg1", 
 "TPHMARCM-1252F_seg1", "TPHMARCM-1275F_seg1", "TPHMARCM-880F_seg1", 
 "TPHMARCM-709F_seg1", "TPHMARCM-746F_seg1", "TPHMARCM-763F_seg1", 
 "TPHMARCM-780F_seg1", "TPHMARCM-054F_seg1", "TPHMARCM-209F_seg1", 
 "TPHMARCM-594F_seg1", "TPHMARCM-649F_seg2", "DvGlutMARCM-F1538_seg1", 
 "TPHMARCM-M001578_seg001", "TPHMARCM-M001611_seg001", "TPHMARCM-M001694_seg001", 
 "TPHMARCM-1044M_seg1", "TPHMARCM-1048M_seg1", "TPHMARCM-1106M_seg1", 
 "TPHMARCM-606M_seg1", "GadMARCM-F000648_seg001", "TPHMARCM-737F_seg1", 
 "TPHMARCM-614F_seg1", "DvGlutMARCM-F1498_seg1", "DvGlutMARCM-F1651_seg1"
 )
```

Collect the clusters that correspond to AMMC-IVLP PN1 neurons and plot the exemplars.
```{r AMMCIVLPPN1-cl, custom.plot=TRUE, cache=TRUE}
ammcivlppn1cl=subset(clusterp0, item%in%ammcivlppn1)$cluster
clear3d()
op=structure(list(FOV = 0, userMatrix = structure(c(1, 0, 0, 0, 0, -1, 0, 0, 0, 0, -1, 0, 0, 0, 0, 1), .Dim = c(4L, 4L)), scale = c(1, 1, 1), zoom = 0.573004126548767), .Names = c("FOV", "userMatrix", "scale", "zoom"))
par3d(op)
drawRegionSurf(c("IVLP_L", "IVLP_R", "AMMC_L", "AMMC_R"), alpha=0.3, FCWBNP.surf)
plot3d(apres16k.p0, 'exem', clusters=ammcivlppn1cl, soma=T)
```

It corresponds to these clusters `r unique(ammcivlppn1cl)`, and  `r length(subset(clusterp0, cluster%in%unique(ammcivlppn1cl))$item)` neurons.

Plot all neurons.
```{r AMMCIVLPPN1-clall, custom.plot=TRUE, cache=TRUE}
clear3d()
par3d(op)
plot3d(apres16k.p0, 'all', clusters=unique(ammcivlppn1cl), soma=T)
```
